EC50 calculation + calculation and upload

### 2018-08-02 R/EC50aggregation.Rmd
added french psm

# variables
cachedir = '/home/andreas/Documents/Projects/species-sensitivity/cache'
fundir = '/home/andreas/Documents/Projects/species-sensitivity/functions'
plotdir = '/home/andreas/Documents/Projects/species-sensitivity/plots'
srcdir = '/home/andreas/Documents/Projects/species-sensitivity/src'

@@

# Load substances
```{r subst1}
## load data
psm = readRDS(file.path(cachedir, 'psm1.rds')) # created in EC50sensitivity_data.Rmd
psm = psm[ !is.na(casnr) ] # only metabolite and sumed pesticides
psm = psm[ !subst_name %in% c('Desethylsimazin') ] # casnr: 1007289; duplicated with Desethylsimazin

## for Nadin and verena
# psm = fread('/home/andreas/Documents/data/romania/det_compounds_with_CAS.csv')
# psm[ , casnr := gsub('-', '', cas) ]
# psm[ , `:=`
#      (variable_id = NA,
#       subst_name = NA,
#       psm_type = NA)]

>>>>

# variables
cachedir = '/home/andreas/Documents/Projects/species-sensitivity/cache'
fundir = '/home/andreas/Documents/Projects/species-sensitivity/functions'
plotdir = '/home/andreas/Documents/Projects/species-sensitivity/plots'
srcdir = '/home/andreas/Documents/Projects/species-sensitivity/src'
datadir = '/home/andreas/Documents/Projects/etox-base/data'

@@

# Load substances
```{r subst1}
## (1) bfg_monitoring pesticides
psm_bfg = readRDS(file.path(cachedir, 'psm1.rds')) # created in EC50sensitivity_data.Rmd
psm_bfg = psm_bfg[ !is.na(casnr) ] # only metabolite and sumed pesticides
psm_bfg = psm_bfg[ !subst_name %in% c('Desethylsimazin') ] # casnr: 1007289; duplicated with Desethylsimazin
psm_bfg[205, cas := '72490-01-8'] # bug (instead of 72490-0-1--8)

## (2) French pesticides
# obtained from Mira
psm_mi = fread(file.path(datadir, 'missingVal.FR.csv'))
psm_mi[ , cas := casconv(casnr)] # convert to CAS
psm_mi = psm_mi[!cas %in% psm_bfg$cas]

## (3) for Nadin and verena
# psm = fread('/home/andreas/Documents/data/romania/det_compounds_with_CAS.csv')
# psm[ , casnr := gsub('-', '', cas) ]
# psm[ , `:=`
#      (variable_id = NA,
#       subst_name = NA,
#       psm_type = NA)]

# combine data.frame
psm = rbindlist(list(psm_bfg, psm_mi), fill = TRUE)
